
\documentclass[en,11pt]{aghdpl}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

% dodatkowe pakiety
\usepackage{enumerate}
\usepackage{listings}
\usepackage{framed}
\lstloadlanguages{TeX}

\lstset{
  literate={ą}{{\k{a}}}1
           {ć}{{\'c}}1
           {ę}{{\k{e}}}1
           {ó}{{\'o}}1
           {ń}{{\'n}}1
           {ł}{{\l{}}}1
           {ś}{{\'s}}1
           {ź}{{\'z}}1
           {ż}{{\.z}}1
           {Ą}{{\k{A}}}1
           {Ć}{{\'C}}1
           {Ę}{{\k{E}}}1
           {Ó}{{\'O}}1
           {Ń}{{\'N}}1
           {Ł}{{\L{}}}1
           {Ś}{{\'S}}1
           {Ź}{{\'Z}}1
           {Ż}{{\.Z}}1
}

%---------------------------------------------------------------------------

\author{Piotr Szmigielski}
\shortauthor{P. Szmigielski}

\titlePL{Implementacja algorytmów dla systemów Monroe i Chamberlina-Couranta z nieliniową funkcją satysfakcji}
\titleEN{Implementation of algorithms for Monroe and Chamberlin-Courant systems under nonlinear satisfaction function}

\shorttitlePL{Implementacja algorytmów dla systemów Monroe i Chamberlina-Couranta z nieliniową funkcją satysfakcji}
\shorttitleEN{Implementation of algorithms for Monroe and Chamberlin-Courant systems under nonlinear satisfaction function}

\thesistype{Master of Science Thesis}

\supervisor{Piotr Faliszewski, PhD}

\degreeprogramme{Computer Science}

\date{2015}

\department{Department of Computer Science}

\faculty{Faculty of Computer Science, Electronics and Telecommunications}


\setlength{\cftsecnumwidth}{10mm}

%---------------------------------------------------------------------------

\usepackage{array}
\newcolumntype{C}[1]{>{\centering\arraybackslash\hspace{0pt}}m{#1}}

\begin{document}

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\let\cleardoublepage\clearpage
\def\bibname{References}
\def\listtablename{List of Tables}
\def\tablename{Table}

\titlepages

\tableofcontents

\include{rozdzial1}
\include{rozdzial2}
\include{rozdzial3}
\include{rozdzial4}
\include{rozdzial5}
\include{rozdzial6}
\include{rozdzial7}

% itd.
% \appendix
% \include{dodatekA}
% \include{dodatekB}
% itd.


\addcontentsline{toc}{chapter}{\bibname}
\bibliographystyle{alpha}
\bibliography{bibliografia}
\begin{thebibliography}{1}

\bibitem{1}
B. Chamberlin and P. Courant. Representative deliberations and representative decisions: Proportional representation and the borda rule. {\em American Political Science Review}, 77(3):718-733, 1983.

\bibitem{2}
B. Monroe. Fully proportional representation. {\em American Political Science Review}, 89(4):925-940, 1995.

\bibitem{3}
P. Skowron, P. Faliszewski and A. Slinko. Achieving Fully Proportional Representation is Easy in Practice. arXiv:1301.6400 [cs.MA], 2013.

\bibitem{4}
P. Skowron, P. Faliszewski and A. Slinko. Achieving Fully Proportional Representation: Approximability Results. arXiv:1312.4026 [cs.AI], 2013.

\end{thebibliography}

\addcontentsline{toc}{chapter}{\listtablename}
\listoftables

\end{document}
